---
title: "Assignment 2 R data exploration"
output:
  html_notebook: default
  html_document: default
---

```{r, include=FALSE}
Sys.setenv("plotly_username"="linus.austen.mcmanamey")
Sys.setenv("plotly_api_key"="3tqgEzyZAGTIeFY5sQ1T")
library(rgl)
```
# physics of cricket
### cricket ball coefficient of restitution
- C_O_R <- 0.42
### effect on velocity of ball
- PRE_BOUNCE_DRAG <- 0.88
### speed of ball after bounce from release
- REBOUND_SPEED_COEFF <- 0.45
### drag for after bounce 
- AFTER_BOUNCE_DRAG <- 0.93
```{r}
C_O_R <- 0.42
PRE_BOUNCE_DRAG <- 0.88
REBOUND_SPEED_COEFF <- 0.45
AFTER_BOUNCE_DRAG <- 0.93
```

```{r}
df <- read.csv("pitch_data.csv")
df$TimeBowled.1  <- NULL
```

# Bounce speed measurements with drag coeff comparison
- set up bSpeed_control as the control variable
- compare bounce speed against the control speed
- create percentage of difference for later calculations

```{r}
df$bSpeed_control <- df$releaseSpeed * PRE_BOUNCE_DRAG
df$bSpeedDiff <- df$bSpeed_control - df$bounceSpeed
df$bSpeedPercent <- (df$bSpeedDiff / df$bSpeed_control)*100
```

## Bounce height measurements using C_O_R for comparsion
- set up comparsion with stump height

```{r}
df$bStumps_control <- df$releaseZ * C_O_R
df$bstumpsDiff <- df$bStumps_control - df$stumpPosZ
df$bBouncePercent <- (df$bstumpsDiff / df$bStumps_control)*100
```

## Stump speed measurements
- create control speed based on coefficents
```{r}
df$sSpeed_control <- df$releaseSpeed * PRE_BOUNCE_DRAG * AFTER_BOUNCE_DRAG
```


```{r}
callGRaph <-function(cleaned, ball_Size, title_String, graph_Name)
{
  p <- plot_ly()
  p <- add_trace(p, x =cleaned$releaseX, y = cleaned$releaseY, z = cleaned$releaseZ, colors = "blue", mode = "markers",  name = 'Release',type = "scatter3d", mode = "markers", marker = list(opacity = 1, size = ball_Size, line=list(color='red', width=1)))
  p <- add_trace(p, x =cleaned$bounceX, y = cleaned$bounceY, z = cleaned$bounceZ, colors = "blue", mode = "markers", name = 'Bounce', type = "scatter3d", mode = "markers", marker = list(opacity = 1, size = ball_Size, line=list(color='green', width=1)))
  p <- add_trace(p, x =cleaned$stumpPosX, y = cleaned$stumpPosY, z = cleaned$stumpPosZ, colors = "blue", mode = "markers",  name = 'Stumps', type = "scatter3d", mode = "markers", marker = list(opacity = 1, size = ball_Size, line=list(color='yellow', width=1)))%>% layout(title = title_String, scene = list(aspectmode = 'data'))
chart_link = plotly_POST(p, filename=paste("scatter3d/", graph_Name))
p
return(chart_link)
}
```
# Test - Lowest bounce 25% of bowling from northern end
```{r}
ball_Size <- 4
graph_Name <- "BounceNend25"
BowlEnd <- "north"
title_String <- paste("Lowest bounce - 25% balls bowled from the ", BowlEnd, " end")
quantileValue <- .75
quantile <- quantile(df$bBouncePercent, quantileValue)
cleaned <- df[df$bBouncePercent >= quantile,]
cleaned <- cleaned[cleaned$bowlerEnd == BowlEnd,]
callGRaph(cleaned, ball_Size, title_String, graph_Name)
```
https://plot.ly/~linus.austen.mcmanamey/436/lowest-bounce-25-balls-bowled-from-the-north-end/


# Test -  Slowest bowling speed 25% of bowling from northern end
```{r}
ball_Size <- 4
graph_Name <- "SlowNend25"
title_String <- paste("Slowest speed - 25% balls bowled from the ", BowlEnd, " end")
quantileValue <- .75
quantile <- quantile(df$bSpeedPercent, quantileValue)
BowlEnd <- "north"
cleaned <- df[df$bSpeedPercent >= quantile,]
cleaned <- cleaned[cleaned$bowlerEnd == BowlEnd,]
callGRaph(cleaned, ball_Size, title_String, graph_Name)
```

https://plot.ly/~linus.austen.mcmanamey/438/slowest-speed-25-balls-bowled-from-the-north-end/

















